\section{Experience}

\runsubsection{Nationale-Nederlanden}
\descript{| Chief IT Architect }
\location{ January 2024 – until now | Warsaw, Poland}
Responsibilities:
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item leading Architecture Guild,
\item acting as Enterprise Architect,
\item collaborating in an international environment with architects and heads of application engineers,
\item advising and contributing to regulatory projects,
\item working with external suppliers.
\end{tightemize}
\sectionsep

\runsubsection{Nationale-Nederlanden}
\descript{| Technical Product Owner of (SRE) Site Reliability Engineering Team }
\location{ October 2022 – December 2023 | Warsaw, Poland}
Planning the backlog of SRE team, as well as working with the team to develop common components that 
are used by entire company, in order to increase their reliability, capabilities and security level. 
Those components are:
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item GitOps tools using ArgoCD,
\item CI / CD processes using Gitlab CI,
\item Kubernetes platform (OKD),
\item libraries and tools used by developers.
\end{tightemize}
\textbf{Stack:} Kubernetes, GitOps, ArgoCD, Helm, GitLab, Docker
\sectionsep

\runsubsection{Nationale-Nederlanden}
\descript{| Software Engineering Lead }
\location{ October 2020 – September 2022 | Warsaw, Poland}
Working as Software Engineering Lead in Scrum Team which is responsible of developing platform for online application for insurance claims.
Moreover:
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item promoting technology guidlines, security and group standards within team,
\item advising PO on technology and specifying backlog, defining non-functional and technology requirements,
\item helping the team to choose the right technology solution,
\item actively participating in IT technology initiatives,
\item introducing software development best practices and suggest improvements to the software development process,
\item participate in developing CI \& CD processes,
\item having influence on architecture of systems developed within Value Stream Team.
\end{tightemize}
\textbf{Stack:} Spring Boot, Kubernetes, GitOps, ArgoCD, Helm, MSSQL, Docker
\sectionsep

\runsubsection{Nationale-Nederlanden}
\descript{| Senior Software Engineer }
\location{ September 2019 – October 2020 | Warsaw, Poland}
Extending the functionality of the document management and satellite systems. 
Working with external company on developing and supporting important internal system. \\
At the same time, I worked as part of \textbf{Site Reliability Engineering} Team on:
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item automation of CI \& CD processes using GitOps approach
\item support developers from different teams in their daily work
\end{tightemize}
\textbf{Stack:} Spring Boot, Kubernetes, GitOps, ArgoCD, Helm, Alfresco, Spock (Groovy), PostgreSQL, Sonar, Jenkins, Docker, Linux, GitLab
\sectionsep

\runsubsection{PwC}
\descript{| Software Developer }
\location{ April 2019 – August 2019 | Warsaw, Poland}
Migration of the legacy system and development of the foundations of the new system in microservice architecture using Domain Driven Design.

\textbf{Stack:} Kotlin, Spring Boot, Hibernate, Spock (Groovy), PostgreSQL, Docker, Linux
\sectionsep

\runsubsection{Raiffeisen Polbank}
\descript{| Java Developer }
\location{ January 2018 – March 2019 | Warsaw, Poland}
Backend development of features related to card payments (Base24, POS / ATM) and internet transfers. 
\begin{tightemize}
\item developing new and migrating legacy systems to Spring Boot in microservices architecture
\item implementation of multi currency card transactions handling
\item implementation of Hystrix into services
\item contribution to the CI / CD processes
\end{tightemize}

\textbf{Stack:} Java 8, Spring Boot, Hystrix, Consul, Vault, PostgreSQL, Redis, Docker, Grafana, Kibana, SonarQube
\sectionsep

\runsubsection{Turbine Analytics}
\descript{| Java Developer + DevOps Lead }
\location{ December 2015 – December 2017 | Warsaw, Poland}
Backend development of the asset management application with high availability and automated deployment.
\begin{tightemize}
\item Implementation of the new backend features in Java.
\item participation in design and implementation of the system architecture. 
\item setting up Cassandra. Modeling Cassandra column families (Stock data).
\item participation in setting up Spark. Implementing simple Spark jobs in Scala. 
\item design and implementation of the external system API.
\item deployment of the system stack with Docker (microservices, databases etc.).
\item setting up continuous delivery process.
\end{tightemize}

\textbf{Stack:} Java 8, Play! Framework, Docker, Swarm, Cassandra, CQL, PostgreSQL, Guice, Scala, Spark, Zeppelin, RabbitMQ, SBT, Git, IntelliJ, Checkstyle, Linux, Spock
\sectionsep

\runsubsection{Turbine Analytics}
\descript{| Junior Java Developer }
\location{ July 2015 – November 2015 | Warsaw, Poland}
\begin{tightemize}
\item Implementation of the new backend features in Java.
\item Third party API Integration (Financial Data).
\item Development of the internal API between microservices.
\item Moved microservice system deployment to Docker containers. Creating docker images and stacks based on the containers.
\end{tightemize}

\textbf{Stack:} Java 8, Play! Framework, Docker, PostgreSQL, Git, IntelliJ, Linux
\sectionsep

\runsubsection{Samsung R\&D Poland}
\descript{| Intern Java Developer }
\location{ May 2014 – June 2015 | Warsaw, Poland}
Implementation of new solutions in the Test Process Support team.
\begin{tightemize}
\item Requirements analysis, developing applications (mostly for Android and Java8) for internal clients, 
\item Automation of test processes,
\item Performance analysis and code inspection.
\end{tightemize}
\textbf{Stack:} Java 8, Android, Kotlin, JavaFX, Git
\sectionsep

\runsubsection{Warsaw University of Technology Business School}
\descript{| IT Helpdesk }
\location{ October 2013 – April 2014 | Warsaw, Poland}
% \begin{tightemize}
% \item Ensuring efficient and reliable operation of all elements of the School internal computer network,
% \item Support for workers. Consultation about hardware, software, computer maintenance , periodic cleaning, archiving resources, 
% \item Ensuring the security of resources of all computers on the network.
% \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \section{Awards} 
 \begin{tabular}{rll}
 Apr 2024	     & 1\textsuperscript{st}/44     & \textbf{Nationale-Nederlanden} - NN International Hackathon \\
 Oct 2023	     & 2\textsuperscript{nd}/13     & \textbf{Nationale-Nederlanden} - NN International Hackathon \\
 Jun 2022	     & 1\textsuperscript{st}/12     & \textbf{Nationale-Nederlanden} - NN International Hackathon \\
 Nov 2021	     & 1\textsuperscript{st}     & \textbf{El Passion x Newonce} - Hackaton \\
 Mar 2017	     & 1\textsuperscript{st}     & \textbf{Allegro BrainCode} - Hackaton \\
 Oct 2015	     & 1\textsuperscript{st}/11  & \textbf{HP Developer Day}  - Hackaton\\
 Oct 2013      & Best Cat.  & President’s scholarship for academic achievements \\
 Feb 2013      & Best Cat.  & President’s scholarship for academic achievements \\
 \end{tabular}
 \sectionsep