%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Marcin}{Łagowski}{ \urlstyle{same}\url{https://www.linkedin.com/in/marcinlagowski} \\
\href{mailto:marcinlagowski92@gmail.com}{marcinlagowski92@gmail.com} | +48 514 010 231
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

%\subsection{Warsaw University of Technology}
\runsubsection{Warsaw University of Technology}
\descript{| Faculty of Electronics and Information Technology}
\sectionsep

\descript{M.Eng. Computer Science}
\location{Expected Feb 2018}
Informatics Systems Engineering
\sectionsep

\descript{B.Eng. Telecommunications}
\location{Graduated Feb 2016 }
Information and Communication Technologies
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Coursework}
%\subsection{Graduate}
%Advanced Machine Learning \\
%Open Source Software Engineering \\
%Advanced Interactive Graphics \\
%Compilers + Practicum \\
%Cloud Computing \\
%\sectionsep
%
%\subsection{Undergraduate}
%Information Retrieval \\
%Operating Systems \\
%Artificial Intelligence + Practicum \\
%Functional Programming \\
%Computer Graphics + Practicum \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
%Unix Tools and Scripting \\
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Languages:}
Java \textbullet{}   
Android \textbullet{} 
Kotlin \textbullet{} 
Scala \\
\location{Databases:}
PostgreSQL \textbullet{}   
Cassandra \textbullet{} 
SQL \\
\location{DevOps:}
Docker \textbullet{} 
Swarm \textbullet{} 
CI \& CD Process\\
\location{Technologies:}
Play! Framework \textbullet{} 
Guice \\
RabbitMQ \textbullet{} 
Spark \textbullet{}
Zeppelin \\
\location{Tools:}
Git \textbullet{} 
Gradle \textbullet{} 
SBT \textbullet{}
IntelliJ \textbullet{}
Checkstyle \
Android Studio \textbullet{} 
Windows \textbullet{} 
Linux \\
\location{Tests:}
JUnit \textbullet{} 
Mockito \textbullet{} 
Spock \\
\sectionsep
\subsection{Languages}
Polish (native) \\
English (B2)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/emlagowski}{\custombold{emlagowski}} \\
LinkedIn://  \href{https://www.linkedin.com/in/marcinlagowski}{\custombold{marcinlagowski}} \\
StackOverflow://  \href{http://stackoverflow.com/users/3233685/marcin-lagowski}{\custombold{marcinlagowski}} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HOBBY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobby}
Football \textbullet{}   
Fantasy books \textbullet{} 
Mobile apps development \textbullet{} 
New technologies \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Raiffeisen Polbank}
\descript{| Java Developer }
\location{ January 2018 – until now | Warsaw, Poland}
\sectionsep

\runsubsection{Turbine Analytics}
\descript{| Java Developer + DevOps Lead }
\location{ December 2015 – December 2017 | Warsaw, Poland}
Backend development of the asset management application. %with high availability and automated deployment.
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Implementation of the new backend features in Java.
\item Participation in design and implementation of the system architecture. 
\item Setting up Cassandra. Modeling Cassandra column families (Stock data).
\item Participation in setting up Spark. Implementing simple Spark jobs in Scala. 
\item Design and implementation of the external system API.
\item Deployment of the system stack with Docker (microservices, databases etc.).
\item Setting up continuous delivery process.
\end{tightemize}
Technologies: Java 8, Play! Framework, Docker, Swarm, Cassandra, CQL, PostgreSQL, Guice, Scala, Spark, Zeppelin, RabbitMQ, SBT, Git, IntelliJ, Checkstyle, Linux, Spock
\sectionsep

\runsubsection{Turbine Analytics}
\descript{| Junior Java Developer }
\location{ July 2015 – November 2015 | Warsaw, Poland}
\begin{tightemize}
\item Implementation of the new backend features in Java.
\item Third party API Integration (Financial Data).
\item Development of the internal API between microservices.
\item Moved microservice system deployment to Docker containers. Creating docker images and stacks based on the containers.
\end{tightemize}
Technologies: Java 8, Play! Framework, Docker, PostgreSQL, Git, IntelliJ, Linux
\sectionsep

\runsubsection{Samsung R\&D Poland}
\descript{| Intern Java Developer }
\location{ May 2014 – June 2015 | Warsaw, Poland}
Implementation of new solutions in the Test Process Support team.
\begin{tightemize}
\item Requirements analysis, developing applications (mostly for Android and Java8) for internal clients,
\item Automation of test processes,
\item Performance analysis, code inspection.
\end{tightemize}
Technologies: Java 8, Android, Kotlin, JavaFX, Git
\sectionsep

\runsubsection{Warsaw University of Technology Business School}
\descript{| IT Helpdesk }
\location{ October 2013 – April 2014 | Warsaw, Poland}
\begin{tightemize}
\item Ensuring efficient and reliable operation of all elements of the School internal computer network,
\item Support for workers. Consultation about hardware, software, computer maintenance , periodic cleaning, archiving resources, 
\item Ensuring the security of resources of all computers on the network.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \section{Awards} 
 \begin{tabular}{rll}
 Mar 2017	     & 1\textsuperscript{st}     & Allegro BrainCode - Hackaton \\
 Oct 2015	     & 1\textsuperscript{st}/11  & HP Developer Day  - Hackaton\\
 Oct 2013	     & Best Cat.  & President’s scholarship for academic achievements \\
 Feb 2013	     & Best Cat.  & President’s scholarship for academic achievements \\
 \end{tabular}
 \sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
